---
title: "Developing Data Products Week2 Assignment"
author: "Pinku"
date: "23 June 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Review criteria
The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
- Does the web page feature an interactive map that appears to have been created with Leaflet?

## Submission

Idea is to create Map which shows Indian cities.Source data has been refered from https://simplemaps.com/

Let’s first load the library Leaflet.

```{r}
library(leaflet)
```

## Indian Cities Map

```{r}
setwd("F:/Data Science Specialization/9 Developing Data Products/Week2/Assignment")
df <- read.csv("IndianCities.csv")
df %>% leaflet() %>%
  addTiles() %>%
  addMarkers(lat = df$lat,lng = df$lng,popup = paste(df$popup, "<br>", "City:", df$city_ascii),clusterOptions =    markerClusterOptions())

```